---
title: "middle east analyses"
author: "Robert Mayer"
date: "12/11/2017"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}

library(dplyr)
library(ggplot2)
library(tidytext)
library(tidyr)
library(igraph)
library(ggraph)
library(wordcloud)

knitr::opts_chunk$set(echo = FALSE)
load("data/corpus.rdata")

corpus %>% 
  filter(!grepl(c("date of foundation"),text)) %>% 
  filter(!grepl(c( "industry"),text)) %>% 
  filter(!grepl(c( "share holders"),text)) -> comments

corpus %>% 
  filter(grepl(("date of foundation+"),
               text)|grepl(( "industry+"),
                           text)|grepl(( "share holders+"),
                                       text)) -> information

```

## activity objectives


## analysed data

`r corpus$company %>% unique() %>% length()`

`r corpus %>% unnest_tokens(word, text, token = "words") %>% select(word) %>% nchar() %>% as.numeric()`

## performed analyses

## results


### sentiment analysis


```{r}
comments %>% 
  unnest_tokens(word,text)-> comments_tidy

#sentiment analysis  
  
lexicon <- get_sentiments("bing")

comments_tidy %>% 
  inner_join(lexicon) %>% 
  count(company,  sentiment) %>%
  spread(sentiment, n, fill = 0) %>%
  mutate(sentiment = positive -negative)-> comments_sentiment

ggplot(comments_sentiment, aes(x = sentiment)) +
  geom_histogram()
```


### wordcloud


```{r}

comments_tidy %>%
  filter(!word %in% stop_words$word) %>%
  count(word) %>%
  with(wordcloud(word, n))
```

### ngram analysis
```{r}
comments %>% 
unnest_tokens(bigram, text, token = "ngrams", n = 2) -> bigram_comments

bigram_comments %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>% 
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  count(word1, word2, sort = TRUE) 


### trigrams

comments %>% 
  unnest_tokens(trigram, text, token = "ngrams", n = 3) -> trigram_comments

trigram_comments %>%
  separate(trigram, c("word1", "word2","word3"), sep = " ") %>% 
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word) %>% 
  filter(!word3 %in% stop_words$word) %>% 
  count(word1, word2, word3, sort = TRUE) 
```

### network analysis


```{r}

information %>% 
  filter(grepl("share holders", text)) %>% 
  mutate(shareholders = gsub("share holders: ","",text)) %>% 
  separate(col = shareholders, into = c("first","second","third"),sep = ";") %>% 
  gather(key = "number",value ="shareholder",-company,-text) %>% 
  filter(!is.na(shareholder)) %>% 
  select(company,shareholder)-> shareholders

graph_from_data_frame(shareholders)-> graph_object

#linking the size of a node to its degree
 

 deg <- degree(graph_object, mode="all")
 V(graph_object)$size <- deg*3
 
 set.seed(30)
 graph_object %>% 
   ggraph() +
   geom_edge_link(alpha = .2) +
   geom_node_point(aes(size = size),alpha = .3) +
   geom_node_text(aes(label = name,size = size), vjust = 1, hjust = 1, check_overlap = FALSE)+
   theme_graph()

```


# qui con filtro cambiamo parametro usato per size dei nodi:
  degree
  accessibility
  betweenness

### data lineage

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



